---
title: "About Databrary"
author: "Rick Gilmore & Andrea Seisler"
date: "`r Sys.time()`"
logo: img/databrary-new-leaf.jpg
output: 
  ioslides_presentation:
    self_contained: false
    widescreen: true    
css: css/ioslides.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda

- Why are we here?
- What is Databrary?
- How can Databrary help your team?
- How to get in touch

---

<iframe width="560" height="315" src="https://www.youtube.com/embed/66oNv_DJuPc" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---

<iframe src="https://databrary.org" height=600px width=1000px>
</iframe>

## What is Databrary?

```{r, echo=FALSE}
db_stats <- databraryapi::get_db_stats()
```

- World's only data library specialized for storing and sharing video and audio
- Hosted at New York University
- Opened 2014
- `r db_stats$institutions` institutions; `r db_stats$investigators + db_stats$affiliates` researchers; `r format(db_stats$hours, digits = 5, decimal.mark=".", big.mark=",", small.mark=".", small.interval=2)` hours of video + other data; `r db_stats$datasets_shared` shared projects

## Databrary's mission

- Accelerate discovery
- Securely share (with restricted audiences of researchers) identifiable data, especially video & audio

## How Databrary protects personal data

- Data shared only with participant permission (& IRB approval)
- [Template language](https://databrary.org/support/irb/release-template.html), scripts and [procedure documentation](https://databrary.org/video/example-video-1.mp4)

## Open sharing (but with restricted audiences)

- Researchers require institutional authorization
- [Formal access agreement](https://databrary.org/about/agreement/agreement.html)
- Site-wide access, not dataset-specific
- Data use and contribution

## Virtues

- Restricted data sharing has long track-record
- Meaningful sharing permission; clarifies nature of risk
- Empowers participants
- Researchers & institutions determine what to share & when

---

- Open, but not public, sharing
- Researchers, Institutions need not reinvent wheels
- More discoverable than personal or project websites
- More secure than public data and materials services or journal web pages

---

- Consistent curation makes reuse easier
- Works for data beyond video
- Secure data interaction via API

---

```{r, echo=TRUE}
databraryapi::get_db_stats()
```

<https://github.com/PLAY-behaviorome/databraryapi>

## How Databrary can help your team

- Home for identifiable data
  - Projects in-process
  - After project/grant has ended
- Home for research procedure videos
  - <https://databrary.org/video/example-video-1.mp4>
- Meet journal/funder sharing requirements & protect data

## Get in touch

- Andrea Seisler <andrea.seisler@databrary.org>
- Rick Gilmore <rog1@psu.edu>

